Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2019-04-21 paper.Rmd
Updated ANZJS paper

---
title: "Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016"
author: "Jeremy Forbes*, Dianne Cook, Rob J Hyndman Department of Econometrics and Business Statistics, Monash University"
wpnumber:
jelcodes: C31, C33, D72
blind: false
cover: false
toc: false
documentclass: anzsauth
bibliography: references.bib
biblio-style: anzsj
classoption: times,doublespace
header-includes: \usepackage{float, bm}
output: 
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    fig_height: 5
    fig_width: 8
---

>>>>

---
title: "Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016"
author: Jeremy Forbes$^*$, Dianne Cook, Rob J Hyndman
toc: false
documentclass: anzsauth
classoption: times, doublespace
fontfamily: times
bibliography: references.bib
biblio-style: anzsj
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: anzjs_preamble.tex
---
